% !TEX program = xelatex

% -----------------------------------------------------------------------------

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper, margin=0.25in]{geometry}
% \usepackage[letterpaper, margin=0.5in]{geometry}

% -----------------------------------------------------------------------------

% Note: Konsole can hover hex codes to see the color

\usepackage[dvipsnames]{xcolor}
\definecolor{headercolor}{HTML}{0b5394} % #0b5394
\definecolor{black}{HTML}{000000} % #000000
\definecolor{gray}{HTML}{b8bfc6} % #b8bfc6

% -----------------------------------------------------------------------------

\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrule}{}

% -----------------------------------------------------------------------------

\usepackage{fontspec}

\newcommand{\fontpath}{./fonts/}
\newfontfamily\mytextfont{JetBrainsMono}[
    Extension      = .ttf,
    UprightFont    = *-Light,
    BoldFont       = *-Bold,
    ItalicFont     = *-Italic,
    BoldItalicFont = *-BoldItalic,
    Path           = \fontpath
]

\newcommand{\customtext}[2]{%
    {\fontsize{#1}{\dimexpr #1pt+2pt}\selectfont #2}%
}

% -----------------------------------------------------------------------------

% Took these from: https://github.com/sumnerevans/resume

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

% -----------------------------------------------------------------------------

\begin{document}

\mytextfont

\begin{flushleft}
    \textcolor{headercolor}{\customtext{20}{Bradley Kenneth Hutchings}} \\
    \customtext{12}{\textit{\customtext{10}{Last Updated: \today}}} \\
    \vspace{14pt}

    % -------------------------------------------------------------------------

    \customtext{10}{(707)-302-9750 | bradleyhutchings@mines.edu | bradley-hutchings.com | breadleaf.github.io} \\
    \customtext{10}{linkedin.com/in/bradley-k-hutchings | github.com/breadleaf | gitlab.com/breadleaf} \\
    \vspace{14pt}

    % -------------------------------------------------------------------------

    \textcolor{headercolor}{\customtext{14}{EDUCATION}}
    \textcolor{gray}{\rule{\textwidth}{2pt}}
    {\customtext{12}{\textbf{Colorado School of Mines} - Golden, CO} \hfill \customtext{12}{May 2025}} \\
    {\customtext{10}{B.S. Computer Science with Computer Engineering Focus} \hfill \customtext{12}{CSCI GPA: 2.97}} \\
    \customtext{10}{Working towards a M.S in Computer Science}
    \vspace{14pt}

    % -------------------------------------------------------------------------

    \textcolor{headercolor}{\customtext{14}{SKILLS}}
    \textcolor{gray}{\rule{\textwidth}{2pt}}
    \begin{tabular}{l|l}
        \customtext{12}{\textbf{Languages}} & \customtext{12}{Python3, C/C++, GoLang, Java, JavaScript, Lua, PSQL, \LaTeX} \\
        \customtext{12}{\textbf{Developer Tools}} & \customtext{12}{Docker, GNU-MAKEFILE, PlatformIO, LLMs + Prompt Engineering} \\
    \end{tabular}
    \vspace{14pt}

    % -------------------------------------------------------------------------

    \textcolor{headercolor}{\customtext{14}{EXPERIENCE}}
    \textcolor{gray}{\rule{\textwidth}{2pt}}

    {\customtext{12}{\textbf{CSM \& NSF REU: Research Internship under Prof. Dong Chen}} \hfill \customtext{12}{June 2024 -> September 2024}} \\
    \customtext{9}{\textit{Assisted graduate student Su Wang. Responsibilities include running tests and summarizing research data.}}
    \vspace{14pt}

    {\customtext{12}{\textbf{Analytical Data Systems: Product Development Internship}} \hfill \customtext{12}{June 2023 -> August 2023}} \\
    \customtext{9}{\textit{Summer field session through Colorado School of Mines working on LLMs and LangChain.}}
    \vspace{14pt}

    {\customtext{12}{\textbf{Computer Engineering Group: Data Engineering Internship}} \hfill \customtext{12}{March 2020 -> June 2020}} \\
    \customtext{9}{\textit{System Admin for short term user data storage server for a mobile technology repair shop.}}
    \vspace{14pt}

    {\customtext{12}{\textbf{FRC \#7667: Robotics Software Engineer}} \hfill \customtext{12}{November 2018 -> June 2019}} \\
    \begin{itemize}
        \item \customtext{9}{\textit{Competed in the 2019 Huston World Championship.}}
        \item \customtext{9}{\textit{Robot drive train and game piece manipulation mechanism programming using C++/WPILIB.}}
    \end{itemize}
    \vspace{14pt}

    % -------------------------------------------------------------------------

    \textcolor{headercolor}{\customtext{14}{PROJECTS}}
    \textcolor{gray}{\rule{\textwidth}{2pt}}

    {\customtext{12}{\textbf{Plummet Language}} \hfill \customtext{12}{January 2023 -> Current}} \\
    \customtext{9}{\textit{An ACM project I lead, currently working on a compiled statically-typed programming language.}}
    \vspace{14pt}

    {\customtext{12}{\textbf{Plummet Language Package Manager}} \hfill \customtext{12}{January 2023 -> Current}} \\
    \customtext{9}{\textit{A package manager for the Plummet Language, using remote git repositories for package hosting.}}
    \vspace{14pt}

    {\customtext{12}{\textbf{Keyboard OS}} \hfill \customtext{12}{May 2023 -> Current}} \\
    \customtext{9}{\textit{An ACM project I lead, aimed at teaching students embedded programming and package management.}}
    \vspace{14pt}

    {\customtext{12}{\textbf{simple\_cpp\_unit\_tests}} \hfill \customtext{12}{June 2023 -> Current}} \\
    \customtext{9}{\textit{A C++ unit test framework focused on being lightweight and easy to use.}}
    \vspace{14pt}

    {\customtext{12}{\textbf{Leaf-Lang}} \hfill \customtext{12}{August 2022 -> Current}} \\
    \customtext{9}{\textit{An interpreted/transpiled procedural dynamically-typed stack-based programming language.}}
    \vspace{14pt}


    {\customtext{12}{\textbf{Cpp-Py}} \hfill \customtext{12}{June 2022 -> Current}} \\
    \customtext{9}{\textit{A C++ header file aimed at teaching students C++ in a familiar syntax.}}
    \vspace{14pt}


    {\customtext{12}{\textbf{Bread Software Repository}} \hfill \customtext{12}{December 2021 -> Current}} \\
    \customtext{9}{\textit{My Gitlab hosted software repository for Arch Linux (compatible with pacman package manager).}}
    \vspace{14pt}

\end{flushleft}

\end{document}
